Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a Vertical-Axis Cross-Flow Turbine

### 2015-04-22 paper.tex
Cite Polagye and Cavagnaro micropower paper
Clarify turbine type in conclusion

Blackwell et al. investigated the effects of Reynolds number on the performance
of a 2 m diameter Darrieus vertical-axis cross-flow wind turbine with NACA 0012
blades \cite{Blackwell1976}. By varying wind tunnel speed, the turbine was made
to operate at approximately constant blade chord Reynolds number $Re_c$ ranging
from $1 \times 10^5$ to $3 \times 10^5$. In this regime the turbine power
coefficient $C_P$ was shown to be sensitive to $Re_c$, with sensitivity
diminishing at the higher Reynolds numbers, especially for turbines of lower
solidity ($Nc/R$, where $N$ is the number of blades and $R$ is the turbine's
maximum radius). More recently, Bravo et al. observed power coefficient of a
straight-bladed VAWT to become Reynolds number independent at $Re_c \approx 4
\times 10^5$.

@@

In this study we determined that, as previously shown, turbine performance
becomes essentially $Re$-independent at a turbine diameter Reynolds number $Re_D
\approx 10^6$, or an approximate blade chord Reynolds number $Re_c \approx 2
\times 10^5$.

>>>>

Blackwell et al. investigated the effects of Reynolds number on the performance
of a 2 m diameter Darrieus vertical-axis cross-flow wind turbine with NACA 0012
blades \cite{Blackwell1976}. By varying wind tunnel speed, the turbine was made
to operate at approximately constant blade chord Reynolds number $Re_c$ ranging
from $1 \times 10^5$ to $3 \times 10^5$. In this regime the turbine power
coefficient $C_P$ was shown to be sensitive to $Re_c$, with sensitivity
diminishing at the higher Reynolds numbers, especially for turbines of lower
solidity ($Nc/R$, where $N$ is the number of blades and $R$ is the turbine's
maximum radius). More recently, Polagye and Cavagnaro observed high Reynolds
number sensitivity for a high solidity helical cross-flow turbine
\cite{Polagye2013b}, and Bravo et al. observed power coefficient of a
straight-bladed VAWT to become Reynolds number independent at $Re_c \approx 4
\times 10^5$.

@@

In this study we determined that, as previously shown, performance for a
high-solidity cross-flow turbine constructed from straight NACA 0020 blades
becomes essentially $Re$-independent at a turbine diameter Reynolds number $Re_D
\approx 10^6$, or an approximate blade chord Reynolds number $Re_c \approx 2
\times 10^5$.
